Distinction Centrality Analysis

### 2025-09-20 analysis.qmd
new data who dis

@@

>>>>

## Political Graphs
```{r Loading TestPolitical Data}
   poli1 <- as.matrix(read.csv(here("Data", "poli1.csv")))
   poli1 <- graph_from_edgelist(poli1, directed = FALSE)
   poli2 <- as.matrix(read.csv(here("Data", "poli2.csv")))
   poli2 <- graph_from_edgelist(poli2, directed = FALSE)
   poli3 <- as.matrix(read.csv(here("Data", "poli3.csv")))
   poli3 <- graph_from_edgelist(poli3, directed = FALSE)
   poli4 <- as.matrix(read.csv(here("Data", "poli4.csv")))
   poli4 <- graph_from_edgelist(poli4, directed = FALSE)
```

@@

## Kite Computational Experiments

```{r}
   # Vary size of kite clique
   # Vary kite density holding clique size constant
```
